% Curriculum Vitae

\documentclass{cv}

%\usepackage[francais]{babel} % Pour les caractres accentus, ...
\usepackage{url}
\usepackage[]{fancyhdr}
\pagestyle{fancy}
\usepackage{amssymb}


%\usepackage[headsep=1cm,headheight=1in]{geometry}

\usepackage{lastpage}

\usepackage{ifthen}

\renewcommand\headrule{}
%\setlength{\topmargin}{16pt} 
%\setlength{\headheight}{12pt} 
%\setlength{\headsep}{25pt} 

\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{}
\rfoot{\thepage}

%\lhead{\ifthenelse{\value{page}=1}{}{Martin L\'evesque}}

\begin{document}
\fontfamily{cmss}\selectfont
% Entte du CV
\entete
%[``Without C, we would have Pasal, Basi and Obol''
%\hspace*{1.5cm}-\hspace{0.3pt}-\hspace{2pt}anonymous]
{Martin L\'evesque}
{6680 Baillargeon\\
Brossard, QC, Canada\\
(438) 394-9110\\
levesque.martin@gmail.com}

% Formation

\section{Summary}
\begin{itemize}
\item Enthusiastic senior software developer with more than 6 years experience in the web industry.
\item Ability and interest to explore quickly emerging technologies.
% \item More than 5 years experience in state-of-the-art research in telecommunications with provincial and national awards, have participated in international internship and postdoc in Europe and USA.
\item Interests on applied research, startups, and open source.
\end{itemize}

\section{Experiences}

\begin{formation}

\item[10/2017 - ...]
     $\cdot$ Web Developer, \textit{Ubisoft}, Montr\'eal, Canada. \\ ~\\

 \begin{itemize}
     \item Internal CI/CD deployment tool (called Publishing Pipeline - PUP) used to deploy Ubisoft games and online services worldwide.
     \item REST and GraphQL APIs design and development.
     \item Main techs used: Node.js, REST, Graphql, Mongodb, redis, Angular, socket.io for streaming events, deployed as Dockerized Microservices, and more.
 \end{itemize}

\item[10/2016 - 10/2017]
     $\cdot$ Concepteur Logiciel Web, \textit{GSI \'Electronique Inc.} (AGCO Corp.), St-Hubert, Canada. \\ ~\\

 \begin{itemize}
     \item Data acquisition and data analysis via smart farming controllers.
     \item Cloud AWS backend of 10-15 servers, big data environment (NoSQL). Mnubo (Big Data company from Montreal) is used to store million of events per day.
     \item Real-time remote visualization via HTML, Angular, and web sockets.
     \item Agile methodology, Atlassian tools (JIRA, Confluence, bitbucket).
     \item Automated tests via Mocha.
     \item Main technologies used: Node.js, Redis, MySql, Angular 1, web sockets, JSON. The backend is fully based on Node.js 6 with REST APIs.
 \end{itemize}

~\newpage

	\item[05/2016 - 10/2016]
     $\cdot$ Senior Web Developer, \textit{Mentel}, Montr\'eal, Canada. \\ ~\\

 \begin{itemize}
     \item Develop and maintain cutting-edge web platforms, mainly using Ruby on Rails, Javascript-Coffeescript, HTML5, CSS3, PostgreSQL.
     \item Monitor the websites performance and fix bugs.
     \item Automated testing.
     \item Exchange with clients to transform requirements into working solutions.
     \item Make time estimate of new projects, schedule monitoring.
 \end{itemize}

   \item[08/2015 - 05/2016]
     $\cdot$ Senior Software Developer, \textit{IOU Financial}, Place Ville Marie (Montr\'eal, Canada). \\ ~\\
     \begin{itemize}
     \item Maintain and develop a loan financial platform. The platform is used by hundreds of financial agents located mainly in USA.
     \item Write RSpec tests while changing or adding functionnalities.
     \item Automated testing with TeamCity (JetBrains) and resolve Quality Assurance (QA) issues with the QA team.
     \item Fix reported bugs.
     \item Software management following an Agile methodology using JIRA (Atlassian) integrated with bitbucket - team of about 10 developers.
     \item Big Data environment - finance framework with thousands of transactions per day.
     \item API integration with third-parties: Canada Post (AddressComplete), Equifax, etc.
     \item \textit{Technologies:} Ruby on Rails, CoffeeScript (and Javascript), RSpec, HAML, HTML5/CSS3, JQuery, MySQL, REST, SOAP, git (bitbucket).
     \end{itemize}\normalsize 

   \item[09/2014 - 08/2015]
     $\cdot$ Postdoctoral Fellow and Visiting Research Assistant, \textit{University of Pittsburgh}, PA, USA. \\ ~\\\small
     Topic: Secured and synchronized internetworking smart grid communications.\normalsize



	\item[2011 - 2014]
     $\cdot$ PhD in Telecommunications, INRS, Montr\'eal, Canada. \\ ~\\
     \small Advanced Fiber-Wireless networks for smart grids: Design, performance modelling (using python), and co-simulation (C++, OMNeT++).  \normalsize   
     
   \item[06/2013 - 09/2013]
     $\cdot$ Research internship, \textit{EDF R\&D}, Clamart, France. \\ ~\\
     \small Topic: Advanced Smart Grid Multi-Simulation. \normalsize
     
   \item[2009 - 2011]
     $\cdot$ Software Developer, \textit{Codency (wordans.com)}, Montr\'eal, Canada. \\ ~\\

\begin{itemize}
\item Software development and optimization of high traffic websites and file sharing systems.
\item \textit{Technologies:} Ruby on Rails, Java, Javascript, HTML/CSS, JQuery, MySQL.
\end{itemize}     
       \normalsize
~\newpage
   \item[2006]
     $\cdot$ Software Developer, \textit{Consortech}, Brossard, Canada. \\ ~\\
     \small Maintain and write softwares managing building plans. Technologies : C, C++. \normalsize
     
   \item[2005]
     $\cdot$ Software Developer, \textit{M.A.G. Integration}, St-Jean-sur-Richelieu, Canada. \\ ~\\
     \small Transactional websites using Magic eDeveloper. \normalsize
\end{formation}



\section{Recent Open Source and Side Projects}

\begin{itemize}
\item \url{https://www.openode.io/} Cloud application platform project allowing to deploy quickly tiny to large websites at low cost. 
\item NPMs: \url{https://www.npmjs.com/~martinlev}.
\item GitHub: \url{https://github.com/martinlevesque}.
\end{itemize}

\section{Computer Skills}

\begin{itemize}
	  \item Advanced software development: Optimization, simulation, mathematical modeling, caching, network and Web programming, etc. 
	  \item Languages: Javascript, Ruby, Elixir, C\# .NET, Python, Coffeescript, C/C++, Matlab, Java, Bash, PHP, etc.
	  \item Backend/frontend Frameworks: Node.js, Ruby on Rails, Phoenix (Elixir), Vue.js, Angular.
	  \item Editors: Atom, vim.
	  \item Automated testing: Mocha.js, expect.js, Minitest, Rspec.
	  \item Containers: Docker, docker-compose, Kubernetes.
	  \item Management: JIRA, Redmine.
	  \item Version control: Git, Mercurial, SVN.
	  \item Relational databases: MySQL, PostgreSQL, MS SQL, Oracle, etc.
	  \item Document databases: MongoDB.
	  \item Key-value store: Redis, memcache.
	  \item Streaming, queuing, messaging: socket.io, kafka, zeromq.
	  \item Operating systems: Linux, Mac, Windows.
\end{itemize}

\newpage

\section{Education}

\begin{formation}
  \item[2011 - 2014]
     $\cdot$ PhD in Telecommunications at Institut National de la Recherche Scientifique (INRS), Universit\'e du Qu\'ebec, Montr\'eal, Canada (\emph{Distinction: Excellent}).
  \item[2008 - 2010]
     $\cdot$ Master in Computer Science
at Universit\'e du Qu\'ebec \`a Montr\'eal (UQAM), Montr\'eal, Canada (\emph{Distinction: Excellent}). 
  \item[2005 - 2007]
    $\cdot$ Bachelor in Computer Science and Software Engineering at Universit\'e du Qu\'ebec \`a Montr\'eal (UQAM), Montr\'eal, Canada.
\end{formation}

\section{Academic Awards and Scholarships}

Most of my research publications are available on Google scholar, \url{https://scholar.google.ca/citations?hl=fr&user=LrKNNfoAAAAJ}.

\begin{formation}
  \item[2014 - 2016]
    $\cdot$ Postdoctoral fellowship. Awarded by \textit{Natural Sciences and Engineering Research Council of Canada (NSERC).}
   \item[2013]
     $\cdot$ SYTACom (McGill University, Canada) International Internship Scholarship.
   \item[2012 - 2014]
     $\cdot$ Doctoral scholarship. Awarded by \textit{Fonds de Recherche du Qu\'ebec - Nature et Technologies} (FRQNT).
   \item[2008 - 2009]
     $\cdot$ Master scholarship. Awarded by \textit{Fonds de Recherche du Qu\'ebec - Nature et Technologies} (FRQNT).
   \item[2008]
     $\cdot$ Bourse d'excellence de la Facult\'e des sciences pour les cycles sup\'erieurs. Awarded by UQAM.
   \item[2007]
     $\cdot$ Undergraduate research scholarship. Awarded by \textit{Natural Sciences and Engineering Research Council of Canada (NSERC)}.
\end{formation}

%\section{References}

%\poste{}{\ }
%\begin{itemize}
%\item Prof. Martin Maier, Institut National de la Recherche Scientifique (INRS), Montr\'eal, Canada. Phone: +1 (514) 228-7024. Email: maier@emt.inrs.ca.
%\item Eric Suignard, Engineer, EDF R\&D, 1, avenue du G\'en\'eral de Gaulle, Clamart, France. Phone: +33 1 47 65 46 43. Email: eric.suignard@edf.fr.
%\item Prof. Halima Elbiaze, Universit\'e du Qu\'ebec \`a Montr\'eal. Phone: (514) 987-3000, office 8485. Email: elbiaze.halima@uqam.ca.
%\end{itemize}

%\section{Computer Skills}
%
%\begin{experience}
%
%	\begin{tasks}
%	  \item Advanced programming: Mathematical modeling, simulation, optimization, caching, network and Web programming, etc. My GitHub, where I share some of my code: \url{https://github.com/martinlevesque}.
%	  \item Programming languages: Python, C/C++, Matlab, Java, Bash, PHP, etc.
%	  \item Version control: Git, SVN.
%	  \item Relational databases: MySQL, Oracle, etc.
%	  \item Operating systems: Linux, Mac, Windows.
%    \end{tasks}
%
%\end{experience}

\end{document}
